Supporting Information

### 2018-03-13 SupportingInformation.Rmd
new file just begun for new surrogate functionality that will support a Taylor's law analyss. Also, minor changes to comments and section structure in supp mat to accommodate a TL analysis

# Question 2 analyses for each dataset

# Question 3 analyses for each dataset

Recall question 3 is: What are the consequences of non-Gaussian copula structure and tail dependence for our understanding of biology and for applications?

**Change of skewness : ** Here, we claim that because of significant tail dependence of the multivariate copula structure, the skewness of the time-series data averaged over all selective locations changed significantly from the individual skewness of time-series data taken at each pairwise location. Spatial mean of the time series data extracts that tail dependence of the multivariate data set, if any, and reflected in the averaged skewness. We tested this with null hypothesis $H_{0}$. If $H_{0}$ is true that means our multivariate copula actually came from normal copula structure with no tail dependence and thus should have the same skewness as of normal copula. So, first we generated $10000$ number of surrogate normal copula from our given multivariate copula keeping the marginal distribution and the correlation (spearman or kendall) same. Then we plotted the distribution of spatial mean of each surrogate time series data set and the given multivariate data. If $p$-value is less than $0.05$, then we reject the null hypothesis in support of significant tail dependence.

@@

## Aphid count \label{skewness_count}

@@

## Aphid first flight \label{skewness_ff}

@@

## North Sea plankton \label{skewness_pns}

@@

## References:

>>>>

# Question 2 analyses for each dataset
Recall that question 2 is: What are some possible causes of non-Gaussian copula structure?

# Question 3 analyses for each dataset
Recall that question 3 is: What are the consequences of non-Gaussian copula structure and tail dependence for our understanding of biology and for applications?

## Skewness of the spatial mean

Here, we claim that because of significant tail dependence of the multivariate copula structure, the skewness of the time-series data averaged over all selective locations changed significantly from the individual skewness of time-series data taken at each pairwise location. Spatial mean of the time series data extracts that tail dependence of the multivariate data set, if any, and reflected in the averaged skewness. We tested this with null hypothesis $H_{0}$. If $H_{0}$ is true that means our multivariate copula actually came from normal copula structure with no tail dependence and thus should have the same skewness as of normal copula. So, first we generated $10000$ number of surrogate normal copula from our given multivariate copula keeping the marginal distribution and the correlation (spearman or kendall) same. Then we plotted the distribution of spatial mean of each surrogate time series data set and the given multivariate data. If $p$-value is less than $0.05$, then we reject the null hypothesis in support of significant tail dependence.

@@

### Aphid count \label{skewness_count}

@@

### Aphid first flight \label{skewness_ff}

@@

### North Sea plankton \label{skewness_pns}

@@

## Extinction risk

## Taylor's law

# References:
